Late Pleistocene stone artefact technology at Mau A, Yen Bai, Northern Vietnam

### 2023-03-22 analysis/paper/paper.Rmd
added new author

---
title: "Late Pleistocene stone artefact technology at Mau A, Yen Bai, Northern Vietnam"
author:
  - Quinn Habedank:
      email: fl@oneoeurhg.edu
      institute: [UofO]
      correspondence: true
  - Ben Marwick:
      email: fl@another.edu
      institute: [UofA]
      correspondence: false
institute:
  - UofO: University of One Place
  - UofA: University of Another Place
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      number_sections: false
      global_numbering: true
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

>>>>

---
title: "Late Pleistocene stone artefact technology at Mau A, Yen Bai, Northern Vietnam"
author:
  - Pham Thanh Son
      email: thanhson9119@gmail.com
      institute: [IofA]
      correspondence: true
  - Quinn Habedank:
      email: fl@oneoeurhg.edu
      institute: [UofO]
      correspondence: true
  - Ben Marwick:
      email: fl@another.edu
      institute: [UofA]
      correspondence: false
institute:
  - IofA: Vien Khao co hoc
  - UofO: University of One Place
  - UofA: University of Another Place
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      number_sections: false
      global_numbering: true
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---
